### 2022-04-27 ms/ms.rmd
Not sure why there are NA in habitat of phylogeny ployt when all habitat is filled our for each species. All dataframes match in size and species so this is ruled out

      # Create the data matrix that can be used to plot data as a heatmap around the phylogeny
      matrix_data <- as.data.frame(data_wide %>%
                  mutate(species_full = gsub("Chinemys reevesii", "Mauremys reevesii", species_full)) %>% 
                  mutate(species_full = gsub("Enithares sp", "Enithares ciliata", species_full))      %>%
                  mutate(habitat = ifelse(species_full == "Pungitius pungitius", "m", habitat))       %>%
                  mutate(habitat = ifelse(species_full == "Danio rerio", "f", habitat))               %>%
                  mutate(trait_category = ifelse(trait_category %in% 
                                                   c("ATPase", "mito_leak", "mito_oxidation"), "Mito. Function", trait_category)) %>%
                  mutate(trait_category = ifelse(trait_category %in% c("endurance", "sprint"), "Performance", trait_category))    %>%
                  mutate(trait_category = ifelse(trait_category %in% c("muscle", "cardiac"), "Muscle Function", trait_category))  %>%
                  mutate(trait_category = ifelse(trait_category %in% c("rest_MR", "max_MR"), "Metabolic Rate", trait_category))   %>%
                  group_by(species_full, trait_category)   %>% 
                  summarise(n = n())                       %>% 
                  spread(trait_category, n, fill = 0))

@@

      # Plot a heatmap of N for each trait around the phylogeny.
      gheatmap(p1, data.matrix(matrix_data2), offset = 1,  
               colnames_position="bottom", legend_title = "N", 
               colnames_angle=45, colnames_offset_y = 0, 
               hjust=0, font.size=2.5, width = 0.35) + 
        scale_fill_viridis(alpha = 0.6) + labs(fill="# of Effects")
```

>>>>

      # Create the data matrix that can be used to plot data as a heatmap around the phylogeny
      matrix_data <- as.data.frame(data_wide %>%
                  mutate(trait_category = ifelse(trait_category %in% 
                                                   c("ATPase", "mito_leak", "mito_oxidation"), "Mito. Function", trait_category)) %>%
                  mutate(trait_category = ifelse(trait_category %in% c("endurance", "sprint"), "Performance", trait_category))    %>%
                  mutate(trait_category = ifelse(trait_category %in% c("muscle", "cardiac"), "Muscle Function", trait_category))  %>%
                  mutate(trait_category = ifelse(trait_category %in% c("rest_MR", "max_MR"), "Metabolic Rate", trait_category))   %>%
                  group_by(species_full, trait_category)   %>% 
                  summarise(n = n())                       %>% 
                  spread(trait_category, n, fill = 0))

@@

      # Plot a heatmap of N for each trait around the phylogeny.
   phylo <-   gheatmap(p1, data.matrix(matrix_data2), offset = 1,  
               colnames_position="bottom", legend_title = "N", 
               colnames_angle=-45, colnames_offset_y = 1,  colnames_offset_x = -0.5,
               hjust=0, font.size=3, width = 0.35) + 
        scale_fill_viridis(alpha = 0.6) + labs(fill="# of Effects")
   phylo
```
